Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-07-21 lowstretch_and_cc.tex
formatting

The method presented in the previous chapter hinges crucially upon our sign generative model. Yet
one can imagine contexts where this model is not applicable, especially when nodes do not represent
human beings. One way to alleviate this issue was introduced with our online algorithm, where this
time, signs are generated by an arbitrary adversary. However, in that case, we are still facing two
limitations\marginpars{limitations is not the right word, maybe \emph{strong constraints}…}
\begin{enumerate}
	\item Our bias remains that the labeling is regular (recall this means informally that the all
		the outgoing signs from a given node tend to be the same, and likewise for the incoming signs),
		since irregularities are the cost payed by the adversary to make our algorithm mispredict. While
		this bias is well suited to social networks, other applications may require other
		bias\marginpars{namely the \pcc{} bias we'll introduce next}.
	\item In the online setting, we evaluate our performance by the regret\marginpars{ref to regret equation},
		whereas in general we are interested in more classical measures of predictive accuracy.
\end{enumerate}

\subsubsection{Experience on directed biological network}
\label{ssub:experience_on_directed_biological_network}

Take for instance a biological network.

@@

\section{Low stretch trees and spanners}
\label{sec:low_stretch_trees_and_spanners}

@@

\input{gtx_algorithm}

@@

\input{gtx_related}

\iffalse
\url{http://www.siam.org/meetings/da17/schedule.html} SODA 13B \url{http://dl.acm.org/citation.cfm?id=3039686}
for instance the Elkin paper \enquote{Our centralized randomized algorithm computes (with
probability close to 1), a $(2k - 1)$-spanner with $n \cdot (1 + O(\frac{\log k}{n}))$ edges in
$O(|E|)$ time, whenever $k = \Omega(\log n)$. Note that when $k = \omega(\log n)$, the number of
edges is $n(1+o(1))$, i.e., in this range the algorithm computes an ultra-sparse spanner in $O(|E|)$
time.} For instance, if $k=5\log n$, we get a $10\log n$-spanner with $n\left(1+O\left(\frac{\log\log
n}{n}\right)\right)$ edges in $O(|E|)$ time.

@@

\begingroup
\small
\setstretch{0.9}
\todos

\setlength\bibitemsep{2pt}
\printbibliography
\endgroup

>>>>

\iffalse
The method presented in the previous chapter hinges crucially upon our sign generative model. Yet
one can imagine contexts where this model is not applicable, especially when nodes do not represent
human beings. One way to alleviate this issue was introduced with our online algorithm, where this
time, signs are generated by an arbitrary adversary. However, in that case, we are still facing two
limitations\marginpars{limitations is not the right word, maybe \emph{strong constraints}…}
\begin{enumerate}
	\item Our bias remains that the labeling is regular (recall this means informally that the all
		the outgoing signs from a given node tend to be the same, and likewise for the incoming signs),
		since irregularities are the cost payed by the adversary to make our algorithm mispredict. While
		this bias is well suited to social networks, other applications may require other
		bias\marginpars{namely the \pcc{} bias we'll introduce next}.
	\item In the online setting, we evaluate our performance by the regret\marginpars{ref to regret equation},
		whereas in general we are interested in more classical measures of predictive accuracy.
\end{enumerate}
\fi

\subsubsection{Experience on directed biological networks}
\label{ssub:experience_on_directed_biological_networks}

\iffalse
Take for instance a biological network.

@@

\iffalse
\section{Low stretch trees and spanners}
\label{sec:low_stretch_trees_and_spanners}

@@

% \input{gtx_algorithm}

@@

% \input{gtx_related}

\url{http://www.siam.org/meetings/da17/schedule.html} SODA 13B \url{http://dl.acm.org/citation.cfm?id=3039686}
for instance the Elkin paper \enquote{Our centralized randomized algorithm computes (with
probability close to 1), a $(2k - 1)$-spanner with $n \cdot (1 + O(\frac{\log k}{n}))$ edges in
$O(|E|)$ time, whenever $k = \Omega(\log n)$. Note that when $k = \omega(\log n)$, the number of
edges is $n(1+o(1))$, i.e., in this range the algorithm computes an ultra-sparse spanner in $O(|E|)$
time.} For instance, if $k=5\log n$, we get a $10\log n$-spanner with $n\left(1+O\left(\frac{\log\log
n}{n}\right)\right)$ edges in $O(|E|)$ time.

@@

\begingroup
\newgeometry{hmargin=2cm,vmargin=1.3cm}
\setstretch{0.9}
\todos

\setlength\bibitemsep{2pt}
\printbibliography
\restoregeometry
\endgroup
